%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Based on the Deedy CV/Resume Template
% XeLaTeX Template
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[10pt,letterpaper]{clar-resume}

\font\fb=''[cmr10]''

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\namesection{Clarissa}{Podell}{ 
(631)~708-2725
~|~ \href{mailto:clarissapodell@gmail.com}{clarissapodell@gmail.com} 
~|~ \href{https://www.linkedin.com/in/clarissapodell/}{in/clarissapodell}
~|~ Valley Stream, NY 11580
}

%----------------------------------------------------------------------------------------
%	SUMMARY
%----------------------------------------------------------------------------------------

\vspace{-1mm}
\section{Summary}
\cvparagraph{Recent Cybersecurity graduate with interests in Vulnerability Research, Binary Exploitation, Reverse Engineering, and Exploit Mitigation.  Experience collaborating in groups and competence in real-world environments through online CTF/wargame challenges and coursework using DETERLab testbeds. Seeking career opportunity to collaborate with like-minded individuals.}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} 

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\subsection{B.S. in Computer Science and}
\subsection{Information Security}
\school{John Jay College of Criminal Justice, City University of New York (CUNY)}
\location{Jan 2016 \textendash{} May 2018 | New York, NY}
\grade{GPA: 4.0 / 4.0}

\sectionspace 

\subsection{B.S. in Fashion Merchandising}
\subsection{Management}
\school{Fashion Institute of Technology, State University of New York (SUNY)}
\location{Aug 2009 \textendash{} May 2013 | New York, NY}
\grade{GPA: 3.48 / 4.0}

\sectionspace

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\subsection{Programming}
\location{Strong:}
Python \textbullet{} C \textbullet{} C++ \textbullet{} {\fb \LaTeX\ } \\ 
\location{Familiar:}
Perl \textbullet{} Assembly (x86 Intel) \textbullet{} Bash  \textbullet{} SML

\smallspace

\subsection{Systems}
Windows \textbullet{} Debian \textbullet{} Ubuntu \textbullet{} Kali Linux

\smallspace

\subsection{Software}
GDB \textbullet{} WinDbg \textbullet{} Immunity Debugger \\ 
OllyDbg \textbullet{} IDA Pro \textbullet{} Visual Studio \textbullet{} GCC \\ 
Wireshark \textbullet{} tcpdump \textbullet{} netcat \textbullet{} Git/SVN \\
Vim \textbullet{} Metasploit \textbullet{} Volatility Framework

\sectionspace

%------------------------------------------------
% Awards
%------------------------------------------------

\section{Awards} 

\subsection{Ruth S. Lefkowitz Mathematics Prize}
\school{John Jay College of Criminal Justice}
\location{May 2018 | New York, NY}
Award presented to one graduating senior for outstanding academic performance in the CS\&IS major.

\smallspace

\subsection{Cornell University's Women in}
\subsection{Technology \& Entrepreneurship}
\subsection{in New York (WiTNY) Scholarship}
\school{John Jay College of Criminal Justice}
\location{2017 - 2018 | New York, NY}
Scholarship for promising female students in technology-related disciplines.

\smallspace

%------------------------------------------------
% Hobbies / Interests
%------------------------------------------------

\section{Hobbies}
\textbullet{} \textbf{Wargames} - OverTheWire, pwnable.kr, Root-Me, SmashTheStack, HackThisSite.\\
\textbullet{} \textbf{Krav Maga} Yellow Belt

%----------------------------------------------------------------------------------------
\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Research / Projects
%------------------------------------------------

\section{Projects}

\runsubsection{Bypassing Microsoft's Control Flow Guard (CFG)}
\school{| Capstone in Cybersecurity}
\location{Sep 2017 \textendash{} Present | John Jay College of Criminal Justice, New York, NY}

Team Lead.  Research vulnerabilities and design limitations in CFG that can be leveraged to circumvent security measures and demonstrate several exploits on CFG-enabled binaries in Windows 10 that hijack control \& gain arbitrary code execution. Publication to be submitted.

\smallspace 

%------------------------------------------------

\runsubsection{Electronic Health Record DApp}
\job{| Faculty Mentored Research: Bitcoin \& Blockchain}
\location{Jan 2018 \textendash{} May 2018 | John Jay College of Criminal Justice, New York, NY}

Research funded by a National Science Foundation grant to develop a infrastructure for distributed health record storage with access managed by a public blockchain.

\smallspace 

%------------------------------------------------
% COURSEWORK
%------------------------------------------------

\runsubsection{Labs (Coursework)}
\school{| Capstone in Cybersecurity} 
\location{Fall 2017 | John Jay College of Criminal Justice, New York, NY}
\vspace{1mm}

\begin{labwork}
\item[\lab{Cryptography Labs:}] 
Factored weak 1024-bit RSA moduli by finding a common divisor and reconstructed the private key to decrypt SSL/TLS traffic; Cracked password hashes with dictionary attacks using Hashcat \& John the Ripper.\\[1pt] 
\item[\lab{Intrusion Detection Systems Lab:}] Configured Snort and OSSEC on a small DETER testbed network and developed signatures \& rules.  Evaluated IDS by creating forged packet streams with Scapy to trigger alerts.\\[1pt]
\item[\lab{Denial of Service Lab:}] Deployed a SYN flood attack between two testbed nodes \& analyzed tcpdump attack traffic to calculate TCP connection durations.\\[1pt] 
\item[\lab{Malware Lab:}] Wrote a proof-of-concept Command \& Control botnet (master and worker) in Python.  Commands: download website, send spam, \& send files from host of choice.\\[1pt] 
\item[\lab{Exploits Lab:}] Wrote scripts to exploit a buffer overflow in web server software and a remote directory traversal vulnerability in perl cgi code.  Created patches to fix the bugs.\\[1pt] 
\item[\lab{OS-Specific security Lab:}] Wrote an exploit in C to bypass Ubuntu's address space layout randomization protection on a binary with a buffer overflow vulnerability.
\end{labwork}

\smallspace % Some whitespace after the section

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Work Experience}

\runsubsection{Head Receptionist \& Admin}
\job{| Williston Park Animal Hospital} \hfill
\dates{06/2014\textendash{}present}
Grows the practice through marketing and strategic partnerships with vendors that support the doctor’s holistic specialty; Implements clinic policies and procedures related to account receivables, billing, collections, and inventory controls; Manage \& direct front-office staff through hiring, interviewing, and training.

\smallspace 

%------------------------------------------------

\runsubsection{Asst. Wholesale Planner}
\job{| alice + olivia, New York, NY} \hfill
\dates{08/2013\textendash{}05/2014}
Worked with the Director of Planning to develop pre-season plans aligned with corporate financial targets; Presented revised sales projections based on current and historical data; Created Excel spreadsheet templates to analyze account sales, stock and profitability across business segments.

\smallspace 

%------------------------------------------------

\runsubsection{Wholesale Intern}
\job{| Alexander Wang Inc., New York, NY} \hfill
\dates{01/2013\textendash{}06/2013}
Researched and identified opportunities to expand wholesale business in Asia and Australia. Coordinated the execution of Fall `13 market week \& supervised a group of interns and temps.

\smallspace
%------------------------------------------------

\runsubsection{Sales}
\job{| Scoop NYC, New York, NY} \hfill
\dates{08/2011\textendash{}08/2013}
Top sales performer, achieved personal monthly quotas averaging \$20,000 in sales per week.  Established loyal network of clients through maintenance of a clientèle database.

\smallspace 

%------------------------------------------------

\runsubsection{Retail Specialist}
\job{| The Kooples, Metro NY Area} \hfill
\dates{08/2012\textendash{}04/2013}
Launched the company's first four stores in the United States.  Oversaw daily operations, established brand recognition \& communicated daily performance to Paris headquarters.

\smallspace 

%------------------------------------------------

\runsubsection{Fashion Office Intern}
\job{| Bloomingdale's, New York, NY} \hfill
\dates{06/2011\textendash{}08/2011}
First intern in history to style seventeen mannequins for the ``Brights and Cropped'' themed story which appeared in the 3rd Ave Flagship windows.

\smallspace 

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}